Simulation of an Attic Fire in a Wood Frame Residential Structure - Chicago, IL

### 2015-05-01 Studies/2012_Chicago/Report/firetech_chicago.tex
Chicago: minor update

\subsection{Assessing the Hazard}
\label{hazard}
A person is susceptible to second-degree burn injuries if skin temperatures exceed 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}. Although firefighters wear protective gear, gear only offers a finite amount of protection. The polycarbonate material in the facepiece of a self-contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}. Structural fire fighting coats and pants are tested to withstand temperatures up to 260~$^{\circ}$C (500~$^{\circ}$F) or 10~kW/m$^2$~\cite{nfpa2013standard} for less than 2.5~min. Exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk. In this case, according the NIOSH report the victim was not wearing gloves or flash hood~\cite{NIOSH:Bowyer}.

>>>>

\subsection{Assessing the Hazard}
\label{hazard}
A person is susceptible to second-degree burn injuries if skin temperatures exceed 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}. Although firefighters wear protective gear, gear only offers a finite amount of protection. The polycarbonate material in the facepiece of a self-contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}. Structural fire fighting coats and pants are tested to withstand temperatures up to 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}. Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk. In this case, according the NIOSH report the victim was not wearing gloves or flash hood~\cite{NIOSH:Bowyer}.
